### 2022-06-30 chapters/literature/draft_citations.tex
rename : images folder

@@

this is \cite{arcuri_practical_2011}

difference tests  \cite{sonnenwald2003evaluating}
%further references 
\cite{lilja2005measuring}
\cite{bukh1992art}
%%%%%%%%%%%%%%%%%
% TODO : REPHRASE THIS other wise it will be plagiarism
list of benchmarks \cite{van_der_kouwe_benchmarking_2018}:
\begin{itemize}
    \item  Not evaluating potential performance degradation
    \item  Benchmark subsetting without proper justification
    \item  Selective data set hiding deficiencies
    \item  Microbenchmarks representing overall performance
    \item  Throughput degraded by x\% => overhead is \%
    \item  Creative overhead accounting
    \item  No indication of significance of data
    \item  Incorrect averaging across benchmark scores
    \item  Benchmarking of simplified simulated system
    \item  Inappropriate and misleading benchmarks
    \item  Same dataset for calibration and validation
    \item  No proper baseline
    \item  Only evaluate against yourself
    \item  Unfair benchmarking of competitors
    \item  Not all contributions evaluated
    \item  Only measure runtime overhead
    \item  False positives/negatives not tested
    \item  Elements of solution not tested incrementally
    \item  Missing platform specification
    \item  Missing software versions
    \item  Subbenchmarks not listed
    \item  Relative numbers only
\end{itemize}
% further references 
\cite{mytkowicz2009producing}
%%%%%%%%%%

@@

%\\\ https://www.cpubenchmark.net/compare/Intel-i7-12700KF-vs-Intel-i7-12700F/4608vs4692 | hardware benchmarking 
\section{energy consumption}

@@

\begin{figure}
    \center{\includegraphics[width=1\linewidth]{images/virtualization_techniques}}
    \caption{Different Methods of Virtualzation}\label{environement:virtualization_technique}
\end{figure}

@@

Based on the studies of \cite{santos2018does}, who analysed the impact of adding the docker layer on the energy consumption.
In their experement. Eddie Antonio et al run multiple benchmarks with and without docker. and compared their energy consumption and execution time.
The first step was to see the impact of docker deamon while there is no work. to see the impact of the orchestrator alone. Later they had the experiment with the following benchmarks
\begin{itemize}
    \item wordpress
    \item reddis
    \item postfresSQL
\end{itemize}
The following figures represents the energy consumption of the system while it is idle. As we can see  in figure \ref{fig:docker_idle} Docker braught arround 1000joules overhead.
\begin{figure}
    \center{\includegraphics[width=.5\linewidth]{images/docker_vs_vm_energy_paper/idle_energy}}
    \caption{energy consumption of Idle system with and without docker \cite{santos2018does}}\label{fig:docker_idle}
\end{figure}
In the other hand as we can see in figure \ref{fig:docker_reddis}. docker increased the execution time of the benchmark by 50 seconds which caused an increase in energy since they are highly correlated.
The authors also highlated the fact that this increase of energy consumption is due to the docker deamon and not the fact that the application is in a container. Moreover they estimted the price of this extra energy and it was less than 0.15\$ in the worst case. Which is non significant compared to the advantages that docker bring for isolation and reproducibility.\\
if we  recap this study in one sentence,it would be the following one.
The dockerised softwares tend to consume more energy, because mainly they take more time to be executed.
The average power consumption is higher with only \textbf{2Watts} and it is due to the docker deamon.This overhead can be up to 5\% for IO intensive application, but it is mearly noticiable when it comes to CPU or DRMA intesive works

\begin{figure}
    \includegraphics[width=.5\linewidth]{images/docker_vs_vm_energy_paper/reddis_time}
    \includegraphics[width=.5\linewidth]{images/docker_vs_vm_energy_paper/reddis_energy}
    \caption{execution time and energy consumption of Redis  with and without docker \cite{santos2018does}}\label{fig:docker_reddis}
\end{figure}

@@

\begin{figure}[!hbt]
    \center{\includegraphics[scale=0.3]{images/greenbenchmarkcycle}}
    \caption{the spiral methode of energy optimization }\label{fig:spirals}
\end{figure}
the aim of this work is to present a set of guidelines to create a benchmarking system to to measure the energy consumption of different programs.
After that, we will use this system to compare the energy consumption of different programming languages. We will extend the work of \citeauthor{pereira2017energy} to a closer distance to production environment by comparing a set of usecases. starting by GRPC framework, and a set of Web Framewroks. Finally we will discuss the impact of the execution environment on the energy consumption of two of the most famous programming languages JAVA and Python. and present how can tunning the Virtual Machine can reduce the energy consumption.

>>>>

Efficiency in energy usage is a well-known topic. In the majority of fields, the purpose is to minimize the energy consumption of electrical devices/components. Modern times even see energy classification (A, B,... F) for Homes, cars and electronic products, to provide the consumer an indication of the energy consumption of his devices, which will reflect on his power bill. This creterions is extended even to the hardware components of computer.
figure\ref{fig:comparaisoncpu} \footnote{\url{https://www.cpubenchmark.net/compare/Intel-i9-12900KS-vs-Intel-i9-12900KF/4813vs4611}}

\begin{figure}
    \includegraphics[width=\linewidth]{imgs/cpu_cost_comparaison}
    \caption{electrical cost comparasion between two cpus }
    \label{fig:comparaisoncpu}
\end{figure}

In computer science, the objective is essentially same.
Numerous studies have been conducted on energy optimization.
Some of these studies concentrate on minimizing energy consumption at the hardware level, while others optimize energy consumption via software.
% displays the digital energy consumption distribution in 2017 \cite{andrae2015global}. ("p" for production and "u" for usage). 
% It demonstrates that both the production and consumption stages have substantial effects.
% In addition, the utilization expenses of data centers, networks, and terminals are also substantial (19 percent , 16 percent and 20 percent respectively).
% TODO : as romain about the graphics for energy distribution

As an example \citeauthor{avgerinou2017trends} evaluated the development of power use effectiveness (PUE) in data centers that belongs to various organizations participating in the European code of conduct for energy efficiency program \cite{avgerinou2017trends}.
The research found a gradual decline in the PUE of data centers, which measures the ratio of the overall energy supplied to the energy used by IT equipment.
A low PUE implies that the majority of energy is utilized to power the data center's IT equipment, while just a little amount is needed for cooling and lighting.

In this thesis, we will place a greater emphasis on the software level in order to decrease the amount of energy that is used. In order to do this, we provide a benchmarking process and a set of tools that are intended to assist practitioners in better comprehending and optimizing the energy usage of their applications.

Thus, Section \ref{sec:energymeasurement}  describes software energy measurements.
It provides examples of hardware and software measuring instruments and describes their differences, benefits, and drawbacks.
It also examines the sources of energy measurement variations, which represent a significant obstacle to achieving precise readings.

@@

definition :benchmark: [noun] something that serves as a standard by which others may be measured or judged.
that serves as a basis for evaluation or comparison (as of computer system performance)
this is \cite{arcuri_practical_2011}

difference tests  \cite{sonnenwald2003evaluating}
%further references 
\cite{lilja2005measuring}
\cite{bukh1992art}
%%%%%%%%%%%%%%%%%
%% generate an introduction for this chapter 
%%%%%%%%%%%%%%%%%
\section{introduction}

list of benchmarks \cite{van_der_kouwe_benchmarking_2018}:
\begin{itemize}
    \item  Not evaluating potential performance degradation
    \item  Benchmark subsetting without proper justification
    \item  Selective data set hiding deficiencies
    \item  Microbenchmarks representing overall performance
    \item  Throughput degraded by x\% => overhead is \%
    \item  Creative overhead accounting
    \item  No indication of significance of data
    \item  Incorrect averaging across benchmark scores
    \item  Benchmarking of simplified simulated system
    \item  Inappropriate and misleading benchmarks
    \item  Same dataset for calibration and validation
    \item  No proper baseline
    \item  Only evaluate against yourself
    \item  Unfair benchmarking of competitors
    \item  Not all contributions evaluated
    \item  Only measure runtime overhead
    \item  False positives/negatives not tested
    \item  Elements of solution not tested incrementally
    \item  Missing platform specification
    \item  Missing software versions
    \item  Subbenchmarks not listed
    \item  Relative numbers only
\end{itemize}
% further references 
\cite{mytkowicz2009producing}
%%%%%%%%%%

@@

%\\\ https://www.cpubenchmark.net/compare/Intel-i7-12700KF-vs-Intel-i7-12700F/4608vs4692 | hardware benchmarking 
\section{energy measurement}\label{sec:energymeasurement}

@@

\begin{figure}
    \center{\includegraphics[width=1\linewidth]{imgs/virtualization_techniques}}
    \caption{Different Methods of Virtualzation}\label{environement:virtualization_technique}
\end{figure}

@@

Based on the studies of \cite{santos2018does}, who analysed the impact of adding the docker layer on the energy consumption.
In their experement. Eddie Antonio et al run multiple benchmarks with and without docker. and compared their energy consumption and execution time.
The first step was to see the impact of docker deamon while there is no work. to see the impact of the orchestrator alone. Later they had the experiment with the following benchmarks
\begin{itemize}
    \item wordpress
    \item reddis
    \item postfresSQL
\end{itemize}
The following figures represents the energy consumption of the system while it is idle. As we can see  in figure \ref{fig:docker_idle} Docker braught arround 1000joules overhead.
\begin{figure}
    \center{\includegraphics[width=.5\linewidth]{imgs/docker_vs_vm_energy_paper/idle_energy}}
    \caption{energy consumption of Idle system with and without docker \cite{santos2018does}}\label{fig:docker_idle}
\end{figure}
In the other hand as we can see in figure \ref{fig:docker_reddis}. docker increased the execution time of the benchmark by 50 seconds which caused an increase in energy since they are highly correlated.
The authors also highlated the fact that this increase of energy consumption is due to the docker deamon and not the fact that the application is in a container. Moreover they estimted the price of this extra energy and it was less than 0.15\$ in the worst case. Which is non significant compared to the advantages that docker bring for isolation and reproducibility.\\
if we  recap this study in one sentence,it would be the following one.
The dockerised softwares tend to consume more energy, because mainly they take more time to be executed.
The average power consumption is higher with only \textbf{2Watts} and it is due to the docker deamon.This overhead can be up to 5\% for IO intensive application, but it is mearly noticiable when it comes to CPU or DRMA intesive works

\begin{figure}
    \includegraphics[width=.5\linewidth]{imgs/docker_vs_vm_energy_paper/reddis_time}
    \includegraphics[width=.5\linewidth]{imgs/docker_vs_vm_energy_paper/reddis_energy}
    \caption{execution time and energy consumption of Redis  with and without docker \cite{santos2018does}}\label{fig:docker_reddis}
\end{figure}

@@

\begin{figure}[!hbt]
    \center{\includegraphics[scale=0.3]{imgs/greenbenchmarkcycle}}
    \caption{the spiral methode of energy optimization }\label{fig:spirals}
\end{figure}
the aim of this work is to present a set of guidelines to create a benchmarking system to to measure the energy consumption of different programs.
After that, we will use this system to compare the energy consumption of different programming languages. We will extend the work of \citeauthor{pereira2017energy} to a closer distance to production environment by comparing a set of usecases. starting by GRPC framework, and a set of Web Framewroks. Finally we will discuss the impact of the execution environment on the energy consumption of two of the most famous programming languages JAVA and Python. and present how can tunning the Virtual Machine can reduce the energy consumption.
